\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2017-12-05 document/tables/sample_properties.tex
Doing number to-dos and update sample comparison
Small update

	\centering
	\begin{tabular}{cccc}
		\hline
		\hline\noalign{\smallskip}
		{} & {Full \textit{Swift} sample} & {Statistical sample} &  {Followed up bursts} \\
		\hline\noalign{\smallskip}
		N$_{BAT}$ & 1071 & 156 & 85\\
		$\log(15-150$keV fluence)  & $-5.9_{-0.7}^{+0.6}$ &  $-5.9_{-0.6}^{+0.7}$ &  $-5.9_{-0.6}^{+0.7}$   \\
		N$_{XRT}$ & 1004 & 154 & 84\\
		$\log(0.3-10$keV flux) & $-12.3_{-0.8}^{+0.7}$ &  $-12.4_{-0.8}^{+0.7}$ &  $-12.4_{-0.6}^{+0.8}$  \\
		N$_{HI}$ & 1034 & 155 & 85\\
		$\log(N_H)$ & $21.4_{-0.5}^{+0.5}$ &  $-21.3_{-0.6}^{+0.6}$ &  $21.4_{-0.7}^{+0.7}$  \\

@@

	\end{tabular}
	\caption{Population properties for the \textit{Swift sample} and the subset of bursts fulfulling the sample criteria. The population characteristics for the three samples exhibit a large degree of similarity, signifying the ability of our selection criteria to effectively capture the underlying population.  \label{tab:sample_properties}}
\end{table*}

>>>>

	\centering
	\begin{tabular}{cccc}
		\hline
		\hline\noalign{\smallskip}
		{} & {Full \textit{Swift} sample} & {Statistical sample} &  {Followed up bursts} \\
		\hline\noalign{\smallskip}
		N$_{BAT}$ & 987 & 156 & 89\\
		$\log(15-150$keV fluence)  & $-5.9_{-0.6}^{+0.7}$ &  $-5.9_{-0.6}^{+0.7}$ &  $-5.9_{-0.7}^{+0.7}$   \\
		N$_{XRT}$ & 909 & 154 & 88\\
		$\log(0.3-10$keV flux) & $-12.3_{-0.8}^{+0.7}$ &  $-12.4_{-0.8}^{+0.7}$ &  $-12.4_{-0.7}^{+0.9}$  \\
		N$_{\mathrm{HI_x}}$ & 250 & 95 & 74\\
		$\log(\mathrm{N}_{\mathrm{HI_x}})$ & $21.7_{-0.9}^{+0.6}$ &  $21.5_{-3.4}^{+0.7}$ &  $21.6_{-4.5}^{+0.7}$  \\

@@

	\end{tabular}
	\caption{Population properties (median and 14th and 86th percentiles as the
	error intervals) for the \textit{Swift sample} and the subset of bursts
	fulfilling the sample criteria. The population characteristics of the three
	samples are very similar, which shows that our selection criteria effectively
	conserve the statistical properties of the underlying population, as least for these parameters.  \label{tab:sample_properties}} \end{table*}
